\newglossaryentry{Controller}{
    name={Controller},
    description={Is a non-physical Actor that can posses a Pawn/Pawn-Derived. It is, in contrast to AIController, used for human player to control pawns.
    In order to controll the character the Posses function is used. },
    plural={}
}


\newglossaryentry{UPROPERTY}{
    name={UPROPERTY},
    description={is placed in front of a Variable declaration in order to make is accessible to the UE},
    plural={}
}

\newglossaryentry{Asset}{
    name={Asset},
    description={
        is just a set of UObjects serialized to disk },
    plural={}
}

\newglossaryentry{Package}{
    name={Package},
    description={
        UPackage is the top-level object inside an asset file and can have many objects inside it
        (somethings like /Game/MyPackage.uobject0 and /Game/MyPackage.uobject1)},
    plural={}
}

\newglossaryentry{Collisio Channel}{
    name={Collision Channel},
    description={
        Defines how the object will react to traces. },
    plural={}
}

\newglossaryentry{Collision Preset}{
    name={Collision Preset},
    description={
        Each Preset contains the Object Type that should be assigned
        and the responses for Trace and Object Channel},
    plural={}
}


\newglossaryentry{Locomotion}{
    name={Locomotion},
    description={Advanced setup for animations with blendspaces},
    plural={}
}


\newglossaryentry{Delegate}{
    name={Delegate},
    description={Binds a function to an event(which is Broadcast).},
    plural={}
}

\newglossaryentry{Collision Response (ECR)}{
    name={ECR},
    description={The Enum ECollisionResponse is made up of Ignore, Overlap and Block and defines how objects collide (interact with each other)},
    plural={}
}

\newglossaryentry{Procedure}{
    name={Procedure},
    description={Function with no return value},
    plural={}
}

\newglossaryentry{Animation Graph}{
    name={Animation Graph},
    description={Contains the logic of the Animation-Blueprint. A State-Machine will determine which animation should be played.},
    plural={}
}

\newglossaryentry{CRTP}{
    name={curiously recurring template pattern},
    description={
        Solves the problem of slicing (of information) by inheriting from a templatet class
        that takes in the defined class as the Template parameter.
        },
    plural={}
}

\newglossaryentry{Animation Modifier}{
    name={Animation Modifier},
    description={},
    plural={}
}

\newglossaryentry{Behavior Trees}{
    name={Behavior Trees},
    description={Stores information about the states you can be in, and actions/tasks to perform depending on those states.},
    plural={}
}

\newglossaryentry{Blackboard}{
    name={Blackboard},
    description={Stores the information for the different branches of the behavior tree to make the decisions},
    plural={}
}

\newglossaryentry{EQS}{
    name={EQS},
    description={Environmental-Query-System },
    plural={}
}

\newglossaryentry{Nav Mesh Volumes}{
    name={Nav Mesh Volumes},
    description={},
    plural={}
}


\newglossaryentry{AI Perception}{
    name={AI Perception},
    description={Sends stiumli(information about what's happening in the surrounding area) to the behavior tree},
    plural={}
}

\newglossaryentry{Cooking}{
    name={Cooking},
    description={
        is the process of converting from an internal asset format to a platform-specific format.},
    plural={}
}

\newglossaryentry{Modal window}{
    name={Modal window},
    description={
        a window that is on top of the main window,
        disables it and must be interacted with first before returning control to the main window},
    plural={}
}

\newglossaryentry{FField}{
    name={FField},
    description={
        Base class for refltion data objects},
    plural={}
}

\newglossaryentry{UMG}{
    name={UMG},
    description={Unreal-Motion-Graphics is a visual UI builder},
    plural={}
}

\newglossaryentry{Slate}{
    name={Slate},
    description={More advanced way to build an interface using C++. instead of the editor and visual scripting},
    plural={}
}

\newglossaryentry{Level Streaming}{
    name={Level Streaming},
    description={Is a Asynchronous level loading mechanism to decrease memory usage by loading and unloading maps dynamically and thus creating seamless worlds},
    plural={}
}

\newglossaryentry{Texture Streaming}{
    name={Texture Streaming},
    description={In essence just LOD for textures. Manages the texture size depending on distance.},
    plural={}
}

\newglossaryentry{Object wild cards}{
    name={Object wild cards},
    description={Are the equivalent to generics in C++. Object Wild Card in Blueprint == Generic in C++},
    plural={}
}

\newglossaryentry{Pool}{
    name={Pool},
    description={Refers to reserved (conceptual) memory and does not relate to acutal taken memory.},
    plural={}
}

\newglossaryentry{SSGI}{
    name={SSGI},
    description={Is a technique to add dynamic indirect lighting. Best use with  lightmass.},
    plural={}
}

\newglossaryentry{Texel}{
    name={Texel},
    description={Is a pixel of the texture map},
    plural={}
}

\newglossaryentry{IES}{
    name={IES},
    description={Illumination Engineering Society }, %TODO:
    plural={}
}

\newglossaryentry{Cached Shadow Map}{
    name={Cached Shadow Map},
    description={}, %TODO:
    plural={}
}

\newglossaryentry{Volumetric Lightmaps}{
    name={Volumetric Lightmaps},
    description={}, %TODO:
    plural={}
}

\newglossaryentry{Bounds}{
    name={Bounds},
    description={Are boxes drawn around the objects.},
    plural={}
}

\newglossaryentry{Gameplay Timer}{
    name={Gameplay Timer},
    description={Schedules actions.},
    plural={}
}

\newglossaryentry{Timer Manager}{
    name={Timer Manager},
    description={Manages all the Gameplay Timer.},
    plural={}
}

\newglossaryentry{streaming distance}{
    name={streaming distance},
    description={},
    plural={}
}

\newglossaryentry{Build rules}{
    name={Build rules},
    description={Script to specify the referenced modules by your custom module},
    plural={}
}

\newglossaryentry{Target rules}{
    name={Target rules},
    description={Script to specify },
    plural={}
}

\newglossaryentry{GameMode}{
    name={GameMode},
    description={Defines the rules of the game (APawn, APlayerController, APlayerState).},
    plural={}
}

\newglossaryentry{Blueprintable}{
    name={Blueprintable},
    description={Is allowed to be used as a base class for blueprints},
    plural={}
}

\newglossaryentry{BlueprintType}{
    name={BlueprintType},
    description={Is allowed to be specified as a variable type in blueprints},
    plural={}
}

\newglossaryentry{RHI}{
    name={\uline{R}endering \uline{H}ardware \uline{I}nterface},
    description={Is allowed to be specified as a variable type in blueprints},
    plural={}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   NIAGARA   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newglossaryentry{Niagara System}{
    name={Niagara System},
    description={Are containers for multiple emitters combined in ONE effect.  },
    plural={}
}

\newglossaryentry{Niagara Emitters}{
    name={Niagara Emitters},
    description={Are containers for Modules. },
    plural={}
}

\newglossaryentry{Niagara Modules}{
    name={Niagara Modules},
    description={Are the base of Niagara VFX. The Modules are built using High-Level-Shading-Language.},
    plural={}
}

\newglossaryentry{Niagara Item}{
    name={Niagara Item},
    description={Is a part of a system or emitter that the user cannot create. Example: system properties, emitter properties and renderers},
    plural={}
}

\newglossaryentry{Niagara Data interface}{
    name={Niagara Data Interface},
    description={Allow access to arbitrary data like mesh data, audio, skeletal mesh data ...},
    plural={}
}

\newglossaryentry{Niagara Stage}{
    name={Niagara Stage},
    description={Is a way to organize the order of execution},
    plural={}
}

\newglossaryentry{Niagara Group}{
    name={Niagara Group},
    description={Is a way to group the data of modules and hence defines the NAMESPACE},
    plural={}
}

\newglossaryentry{Asset Registry}{
    name={Asset Registry},
    description={in memory stored list of unloaded assets. },
    plural={}
}

\newglossaryentry{Character}{
    name={Character},
    description={Pawns that have a mesh, collision, and built-in movement logic},
    plural={}
}


\newglossaryentry{Animation Sequence}{
    name={Animation Sequence},
    description={is an animation for a specific Skeleton},
    plural={}
}


\newglossaryentry{Blend Space}{
    name={Blend Space},
    description={enables you to play different Animation Sequences depending on a given variable (e.g. speed)},
    plural={}
}


\newglossaryentry{Animation Montage}{
    name={Animation Montage},
    description={enables you to add additional logic to Animation Sequences like sound, particle effects, notifcations ...},
    plural={}
}


\newglossaryentry{Component}{
    name={Component},
    description={provides a piece of functionality that can be added to an actor
    and thus do not exist by themselves. Are the only way to render meshes and images
    ,implement collision, play audio ... everything the player sees or interacts with
    in the world. In contrast to sub-objects, components
    instances wihthin an actor will be instanced},
    plural={}
}

\newglossaryentry{bSweep}{
    name={bSweep},
    description={Whether we sweep to the destination location, triggering overlaps along the way and stopping short of the target if blocked by something.},
    plural={}
}


\newglossaryentry{Subsystem}{
    name={Subsystem},
    description={are automatically instanced classes with managed lifetimes.},
    plural={}
}


\newglossaryentry{Blueprint Interface}{
    name={Blueprint Interface},
    description={where you declare functions but leave the implementation to the blueprints that use the interface. So it's just like a interface in programming},
    plural={}
}



\newglossaryentry{Game State}{
    name={Game State},
    description={},
    plural={}
}


\newglossaryentry{Event Dispatcher}{
    name={Event Dispatcher},
    description={Allows a blueprint class to report on its state to the level blueprint},
    plural={}
}


\newglossaryentry{BSP Brush}{
    name={BSP Brush},
    description={is an Actor used to block-out levels. },
    plural={}
}

\newglossaryentry{Primary Asset ID}{
    name={Primary Asset ID},
    description={How to refer to an asset the asset manager is managing.},
    plural={}
}

\newglossaryentry{Data Layer}{
    name={Data Layer},
    description={},
    plural={}
}

\newglossaryentry{Material Layer}{
    name={Material Layer},
    description={is an Asset to create a layer that can be masked or blended with other layers in the material},
    plural={}
}

\newglossaryentry{Material Layer Blend}{
    name={Material Layer Blend},
    description={is an asset to create a mask for blending two layers together},
    plural={}
}

\newglossaryentry{Material Expresiion}{
    name={Material Expresiion},
    description={},
    plural={}
}

\newglossaryentry{World}{
    name={World},
    description={The World is the top level object representing a level or a sandbox in which Actors and Components will exist and be rendered.},
    plural={}
}

\newglossaryentry{Navigation Invocer}{
    name={Navigation Invocer},
    description={},
    plural={}
}

\newglossaryentry{Anim Instance}{
    name={Anim Instance},
    description={Animation, -Sequence, -Montage or -Blueprint derives from the 'UAnimInstance'-Class. Used for character animaations.},
    plural={}
}

\newglossaryentry{Conduit}{
    name={Conduit},
    description={Is a transition rule that can do '1 to many' , 'many to 1' or 'many to many' instead of the simple '1 to 1'},
    plural={}
}

\newglossaryentry{mipmap}{
    name={mipmap},
    description={are pre-calculated, optimized sequences of images, each of which is a progressively lower resolution. MIP(multum in parvo = much in little)},
    plural={}
}

\newglossaryentry{Module}{
    name={Module},
    description={},
    plural={}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%      GAS    %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newglossaryentry{GLS-Avatar}{
    name={GLS-Avatar},
    description={
        Is the physical representation of the ASC},
    plural={}
}

\newglossaryentry{GLS-Owner}{
    name={GLS-Owner},
    description={
        Actor that holds the ASC},
    plural={}
}

\newglossaryentry{ASC}{
    name={ASC},
    description={
        AbilitySystemComponent},
    plural={}
}

\newglossaryentry{Latent Task}{
    name={Latent Task},
    description={
        A task that is executed over multiple frames},
    plural={}
}